\ttlfnt{Comparing the performance of websites and their content distribution networks}

### 2016-08-27 Writeup/paper.tex
Make comment more clear
Additional comment
Add some missing points to the measurement method

% TODOs:
% 	- add a section on the tool, what it does and how it tries to ensure accuracy and repeatability in our dynamic environment (throughput and ping tests beforehand, repeating each run 3 times, re-try logic to make the code robust etc. etc. Just sell it!)
% 	- (Sub?)Section on the data we collect and why this information is useful for our study
\section{Method}\label{sec:method}
\subsection{Measurement and tools}
% Possible improvements / modifications:
% "owner of the web page" -> organisation hosting the webpage?
% Why 3000 packets?
% We also do a ping test at the start to ensure that latency is in a reasonable range (< 150 ms)
%
%

To measure the performance of CDNs, we have created a tool to automatically capture various quantitative and qualitative performance metrics when given a list of URLs to online video or audio content. In order to compare the performance of CDNs to that of the websites that present the content, we measure 2 primary quantitative metrics: Ping or Round-trip-time and the number of hops required to reach the server. We also measure the throughput to the CDN. To gain further insight into the potential causes for variances in performance, we also take note of the location and owner of the web page and CDN IPs.

Our tool is written using Python 3, but makes use of a number of third-party tools and services. It makes use of the youtube-dl\footnote{youtube-dl: available at https://rg3.github.io/youtube-dl/} tool to download multimedia content (which is used to measure bandwidth, as detailed below), and uses tcpdump to passively capture network traffic (on Windows we use WinDump which is a Windows port of tcpdump, but for the purposes of this report we will refer to tcpdump). The ipinfo.io service\footnote{ipinfo: available at http://ipinfo.io/} is used to gather information about the registered owners of the website and CDN IP addresses.

For each input URL we run youtube-dl and ask that it simply return the URL of the actual content and exit. Both URLs are resolved to IP addresses and stored for later measurement. We then run tcpdump, specifying that it will terminate after 3000 packets have been received, and then run youtube-dl again. This time we let youtube-dl actually download the media file, allowing tcpdump to capture the required 3000 packets and then terminate. At this point we can kill the youtube-dl process and just consider its output. First, we look at the last line of output from youtube-dl in order to get the throughput that the content was transmitted at. This does mean that we rely on youtube-dl's measurements being accurate, but previous attempts to measure throughput ourselves proved inaccurate as youtube-dl does some work before downloading (for example to get the CDN URL from the webpage).

@@

In order to reduce the chance of our results being affected by other applications that might be using the network, we first listen to the existing traffic on the network when the tool first starts up. If there is more than 100KB/s of incoming traffic or more than 30KB/s of outgoing traffic, we prompt the user to reduce network traffic and do not proceed with the test. This gives our results greater accuracy and repeatability as it prevents us from running the experiment when there is already high-network usage, which would skew the data.

@@

\section{Results}\label{sec:results}
\subsection{Home network}
% We are missing the caching train in this section wrt unpopular video (since the same video is used)
% Telkom is first -> EU -> Telkom -> Telkom
% Then ISP 2 is second -> Google Cache -> ISP 2 -> ISP 2
% Then ISP 3 is third -> Google Cache -> ISP 3 -> ISP 3
% Then ISP 4 is fourth but uses same backbone as ISP 3 so -> ISP 3 -> ISP 3 -> ISP 3 etc.

>>>>

\section{Method}\label{sec:method}
\subsection{Measurement and tools}
% We should mention that on testing YouTube dl performed the same as streaming through browser.
%

To measure the performance of CDNs, we have created a tool to automatically capture various quantitative and qualitative performance metrics when given a list of URLs to online video or audio content. In order to compare the performance of CDNs to that of the websites that present the content, we measure 2 primary quantitative metrics: Ping or Round-trip-time and the number of hops required to reach the server. We also measure the throughput to the CDN. To gain further insight into the potential causes for variances in performance, we also take note of the location and hosting organisation of the web page and CDN IPs. The source code for our tool is publicly available on GitHub\footnote{CDNPerf -  https://github.com/jacquesh/cdnperf}.

Our tool is written using Python 3, but makes use of a number of third-party tools and services. It makes use of the youtube-dl\footnote{youtube-dl: available at https://rg3.github.io/youtube-dl/} tool to download multimedia content (which is used to measure bandwidth, as detailed below), and uses tcpdump to passively capture network traffic (on Windows we use WinDump which is a Windows port of tcpdump, but for the purposes of this report we will refer to tcpdump). The ipinfo.io service\footnote{ipinfo: available at http://ipinfo.io/} is used to gather information about the organisation that is hosting the website and CDN IP addresses.

For each input URL we run youtube-dl and ask that it simply return the URL of the actual content and exit. Both URLs are resolved to IP addresses and stored for later measurement. We then run tcpdump, specifying that it will terminate after 3000 packets have been received. This is just to gather enough packets that we can be fairly sure that our results are not contaminated by another process using the network at an unfortunate time. We then run youtube-dl again, but this time we let it actually download the media file, allowing tcpdump to capture the required 3000 packets and then terminate. At this point we can kill the youtube-dl process and just consider its output. First, we look at the last line of output from youtube-dl in order to get the throughput that the content was transmitted at. This does mean that we rely on youtube-dl's measurements being accurate, but previous attempts to measure throughput ourselves proved inaccurate as youtube-dl does some work before downloading (for example to get the CDN URL from the webpage).

@@

In order to reduce the chance of our results being affected by other applications that might be using the network, we first ping Google's 8.8.8.8 DNS server and listen to the existing traffic on the network when the tool first starts up. If we get a round-trip time of over 150ms or there is more than 100KB/s of incoming traffic or more than 30KB/s of outgoing traffic, we prompt the user to reduce network traffic and do not proceed with the test. This gives our results greater accuracy and repeatability as it prevents us from running the experiment when there is already high-network usage, which would skew the data.

@@

\section{Results}\label{sec:results}
\subsection{Home network}
% We are missing the caching train in this section wrt unpopular video (since the same video is used)
% This is another reason why 3 tests are run, it makes this caching behaviour clear
% Telkom is first -> EU Google Cache -> Telkom -> Telkom
% Then ISP 2 is second -> SA Google Cache -> ISP 2 -> ISP 2
% Then ISP 3 is third -> SA Google Cache -> ISP 3 -> ISP 3
% Then ISP 4 is fourth but uses same backbone as ISP 3 so -> ISP 3 -> ISP 3 -> ISP 3 etc.
